### 2017-11-22 manuscript.rmd
included mention to loss of palpons a 3rd time with M. claudanielis in text

Palpons are modified mouthless gastrozooids used for digestion and circulation of the gastrovascular fluid. They were present in the MRCA of siphonophores (Figure 5b), retained in most species, but lost twice independently in the branches leading to *Bargmannia* and Calycophorae. These taxa might have found other avenues to effectively circulate nutrients across the colony.

>>>>

Palpons are modified mouthless gastrozooids used for digestion and circulation of the gastrovascular fluid. They were present in the MRCA of siphonophores (Figure 5b), retained in most species, but lost three times independently in the branches leading to *Bargmannia*, in Calycophorans, and in *Marrus claudanielis*. These taxa might have found other avenues to effectively circulate nutrients across the colony.
